


```{r}
#Initiating the librariers that we will need
library(tidyverse)
library(readxl)

# Read the Data
setwd("/Users/jimmy/AnacondaProjects/Data602/Group Project")
Sales = read_excel(path = "Product Sales.xlsx", sheet ="Sales")
```
```{r}
head(Sales)


```



```{r}
# First we can check out the geographic distrubtions of the companies

library(ggplot2)
ggplot(Sales, aes(x=CompanyWorldRegion))+geom_bar()


# Next lets dive deeper into the region and check out revenues 


library(dplyr)
region <- Sales %>%
  group_by(CompanyWorldRegion) %>%
  summarise(mean_total_revenue=mean(AddInRevenue),
            median_total_revenue=median(AddInRevenue),
            n=n()) %>%
  ungroup() %>% 
  arrange(CompanyWorldRegion)



ggplot(region, aes(x=CompanyWorldRegion, y=mean_total_revenue))+geom_point() +scale_y_log10()


head(region)


```



```{r}
#PCA
# to conduct PCA we need all of our features to be of the numeric data type

library(dummies)
cols <- c('CustomerID', 'CompanySize','ExcelAddInItemsSold','ExcelAddInItemsSold','AddInSalesTransactions','TransactionsAutoPay','TransactionsManualPay','AnalyticsSoftwareRevenue' )
newdata <- Sales[cols]

# just checking to make sure it looks good
str(cols)

# generating the PCA
prin_comp <- prcomp(newdata, scale. = T)

summary(prin_comp)
biplot(prin_comp, scale = 0)

std_dev <- prin_comp$sdev
pr_var <- std_dev^2
prop_varex <- pr_var/sum(pr_var)

# visualizing the PCA
plot(prop_varex, xlab = "Principal Component",
             ylab = "Proportion of Variance Explained",
             type = "b")
             
             
plot(cumsum(prop_varex), xlab = "Principal Component",
              ylab = "Cumulative Proportion of Variance Explained",
              type = "b")             
             
             
```


`



#### I could not get a confusion matrix to generate, I tried so many different things from online/stack overflow. I think it has something to do with factor levels being wrong... but I dont know!!!!!!!!

res = neuralnet::compute(NeuralFit, m[,c("pct_loan_income","dti")])
pred_train = round(res$net.result)

library(dplyr)
library(caret)
pred_rowid <- as.numeric(row.names(pred_train))
train_loan <- train %>% filter(row_number(loan_default) %in% pred_rowid) %>% select(loan_default)
confusionMatrix(as.factor(train_loan$loan_default), as.factor(pred_train))

confusionMatrix(
    factor(train_survived$loan_default, levels=1:148),
    factor(pred_train, levels=1:148)
)




Prediction2 <- prediction(NeuralFit, datatest)


table(Prediction2,test$loan_default,drop=F)

library(caret)
confusionMatrix(as.factor(NeuralPredict), as.factor(LendingClub$loan_default)

NeuralFit$result.matrix
NeuralFit$
  
  
  
  
  
  
  
  
```


